---
title: "Project2"
author: "Yiqun Zhao, Zhaosong Yuan, Jiacheng Tan"
date: "2/12/2020"
output: html_document
---

```{r setup, include<-FALSE}
knitr::opts_chunk$set(echo <- TRUE)
```

```{r, echo<-FALSE}
rm(list = ls())
library(data.table)
library(mlogit)
library(gmnl)
library(echarts4r)
```

## Q3: Logit model without segmentation
```{r}
data <- fread('kiwi_bubbles_P2.csv', stringsAsFactors = FALSE)

#Drop observations with stockout
data=data[!(data$price.KB==99),]
data=data[!(data$price.KR==99),]
data=data[!(data$price.MB==99),]

#Now columns 4 through 7 contains "Price.something" info.
mlogitdata <- mlogit.data(data, id.var = "id", varying = 4:7, choice <- "choice", shape = "wide")

#Run MLE.
mle <- gmnl(choice ~ price, data = mlogitdata)
summary(mle)
coef_noseg <- mle$coefficients

demand_KB <- function(price_KB, price_KR, price_MB, param) {
  return(
    exp(param[1] + param[4] * price_KB) / (1 + exp(param[1] + param[4] * price_KB) + exp(param[2] + param[4] * price_KR) + exp(param[3] + param[4] * price_MB))
  )
}

demand_KR <- function(price_KB, price_KR, price_MB, param) {
  return(
    exp(param[2] + param[4] * price_KR) / (1 + exp(param[1] + param[4] * price_KB) + exp(param[2] + param[4] * price_KR) + exp(param[3] + param[4] * price_MB))
  )
}

demand_MB <- function(price_KB, price_KR, price_MB, param) {
  return(
    exp(param[3] + param[4] * price_MB) / (1 + exp(param[1] + param[4] * price_KB) + exp(param[2] + param[4] * price_KR) + exp(param[3] + param[4] * price_MB))
  )
}

prob_KB <- demand_KB(mean(data$price.KB), mean(data$price.KR), mean(data$price.MB), coef_noseg)
prob_KR <- demand_KR(mean(data$price.KB), mean(data$price.KR), mean(data$price.MB), coef_noseg)
prob_MB <- demand_MB(mean(data$price.KB), mean(data$price.KR), mean(data$price.MB), coef_noseg)
```

Own elasticities for all combination of products:
```{r}
ownElasticity_KB <- -coef_noseg[4] * mean(data$price.KB) * (1 - prob_KB)
ownElasticity_KR <- -coef_noseg[4] * mean(data$price.KR) * (1 - prob_KR)
ownElasticity_MB <- -coef_noseg[4] * mean(data$price.MB) * (1 - prob_MB)
cat(sprintf('Own elasticity of KB is %.2f\nOwn elasticity of KR is %.2f\nOwn elasticity of MB is %.2f', ownElasticity_KB, ownElasticity_KR, ownElasticity_MB))
```
As we can see from the result of above, all products' demand is elastic.


Cross-price elasticities for all combination of products:
```{r}
crossElasticity_KBvsKR <- -coef_noseg[4] * mean(data$price.KR) * prob_KR
crossElasticity_KBvsMB <- -coef_noseg[4] * mean(data$price.MB) * prob_MB
crossElasticity_KRvsKB <- -coef_noseg[4] * mean(data$price.KB) * prob_KB
crossElasticity_KRvsMB <- -coef_noseg[4] * mean(data$price.MB) * prob_MB
crossElasticity_MBvsKB <- -coef_noseg[4] * mean(data$price.KB) * prob_KB
crossElasticity_MBvsKR <- -coef_noseg[4] * mean(data$price.KR) * prob_KR
cat(sprintf('Cross-price elasticiy of KB and KR is %.2f\nCross-price elasticiy of KB and MB is %.2f\nCross-price elasticiy of KR and KB is %.2f\nCross-price elasticiy of KR and MB is %.2f\nCross-price elasticiy of MB and KB is %.2f\nCross-price elasticiy of MB and KR is %.2f\n', crossElasticity_KBvsKR, crossElasticity_KBvsMB, crossElasticity_KRvsKB, crossElasticity_KRvsMB, crossElasticity_MBvsKB, crossElasticity_MBvsKR))
```
As shown above, the cross-price elasticity of any two products with the product left is equal. It's not a surprise, as we can see from the function to calculate the cross-price elasticity, the input only concerns the product which is denominator.


```{r}
#Unit cost
uc <- 0.5
pricespace_KB <- seq(.01, 3, .01)
pricespace_KR <- seq(.01, 3, .01)
#Profit case 1
#"demand" function represents each individual consumer's choice probability.
#In order to calculate profit, we multiply the "demand" by the number of consumers.
profit_KB <- outer(pricespace_KB, pricespace_KR, function(x, y) return(1000 * demand_KB(x, y, 1.43, coef_noseg) * (x - uc)))
profit_KR <- outer(pricespace_KB, pricespace_KR, function(x, y) return(1000 * demand_KR(x, y, 1.43, coef_noseg) * (y - uc)))
profit <- profit_KB + profit_KR
index <- which(profit == max(profit), arr.ind = TRUE)
optimal_KBprice <- pricespace_KB[index[1]]
optimal_KRprice <- pricespace_KR[index[2]]
optimal_KBprice
optimal_KRprice
```
The optimal prices to achieve maximum profit for Kiwi company is to set the price of KB to 1.16 and the price of KR to 1.16.




## Q4: Logit model with segmentation
```{r}
demo <- fread('demo_P2.csv', stringsAsFactors = FALSE)

#Find the optimal K value.
wss <- numeric()
for (i in 1:15) {
  wss <- c(wss, sum(kmeans(x = demo[,2:18], centers = i, nstart = 1000)$withinss))
}
plot(1:15, wss, type = 'b', xlab = 'Number of Clusters', ylab = 'Within Groups Sum of Squares')

```

According to the elbow method, I choose 8 as the cluster number.

```{r}
demo_cluster <- kmeans(x = demo[,2:18], centers = 8, nstart = 1000)
cluster_id <- data.frame(id = demo$id, cluster = demo_cluster$cluster)
data <- merge(data, cluster_id, by = 'id', all.x = TRUE)
data$cluster[is.na(data$cluster)] <- 9

# segment share
seg.share <- c(table(demo_cluster$cluster), 359 - sum(table(demo_cluster$cluster))) / 359

coef_seg <- data.frame(segment = 1:9, intercept.KB = NA, intercept.KR = NA, intercept.MB = NA, price.coef = NA)
for (i in 1:9) {
  data_sub <- subset(data, cluster == i)
  mlogitdata <- mlogit.data(data_sub, id.var = 'id', varying = 4:7, choice = 'choice', shape = 'wide')
  mle <- gmnl(choice ~ price, data = mlogitdata)
  cat(sprintf('\n\n**************************\n>>>Segment %d:<<<\n', i))
  print(summary(mle))
  coef_seg[i, -1] <- mle$coefficients
}

prob_KB_seg <- apply(coef_seg[,-1], MARGIN = 1, function(x) demand_KB(mean(data$price.KB), mean(data$price.KR), mean(data$price.MB), x))
prob_KR_seg <- apply(coef_seg[,-1], MARGIN = 1, function(x) demand_KR(mean(data$price.KB), mean(data$price.KR), mean(data$price.MB), x))
prob_MB_seg <- apply(coef_seg[,-1], MARGIN = 1, function(x) demand_MB(mean(data$price.KB), mean(data$price.KR), mean(data$price.MB), x))

prob_KB_seg_aggre <- sum(seg.share * prob_KB_seg)
prob_KR_seg_aggre <- sum(seg.share * prob_KR_seg)
prob_MB_seg_aggre <- sum(seg.share * prob_MB_seg)
```

Own elasticities for all combination of products under segments:
```{r}
ownElasticity_KB_seg <- -(mean(data$price.KB) / prob_KB_seg_aggre) * sum(seg.share * coef_seg[,5] * prob_KB_seg * (1 - prob_KB_seg))
ownElasticity_KR_seg <- -(mean(data$price.KR) / prob_KR_seg_aggre) * sum(seg.share * coef_seg[,5] * prob_KR_seg * (1 - prob_KR_seg))
ownElasticity_MB_seg <- -(mean(data$price.MB) / prob_MB_seg_aggre) * sum(seg.share * coef_seg[,5] * prob_MB_seg * (1 - prob_MB_seg))
cat(sprintf('Own elasticity of KB under segments is %.2f\nOwn elasticity of KR under segments is %.2f\nOwn elasticity of MB under segments is %.2f', ownElasticity_KB_seg, ownElasticity_KR_seg, ownElasticity_MB_seg))
```
The own elasticity of all products is a little bit smaller than the no-segmentation case.

Cross-price elasticities for all combination of products under segments:
```{r}
crossElasticity_KBvsKR_seg <- -(mean(data$price.KR) / prob_KB_seg_aggre) * sum(seg.share * coef_seg[,5] * prob_KB_seg * prob_KR_seg)
crossElasticity_KBvsMB_seg <- -(mean(data$price.MB) / prob_KB_seg_aggre) * sum(seg.share * coef_seg[,5] * prob_KB_seg * prob_MB_seg)
crossElasticity_KRvsKB_seg <- -(mean(data$price.KB) / prob_KR_seg_aggre) * sum(seg.share * coef_seg[,5] * prob_KB_seg * prob_KR_seg)
crossElasticity_KRvsMB_seg <- -(mean(data$price.MB) / prob_KR_seg_aggre) * sum(seg.share * coef_seg[,5] * prob_MB_seg * prob_KR_seg)
crossElasticity_MBvsKB_seg <- -(mean(data$price.KB) / prob_MB_seg_aggre) * sum(seg.share * coef_seg[,5] * prob_KB_seg * prob_MB_seg)
crossElasticity_MBvsKR_seg <- -(mean(data$price.KR) / prob_MB_seg_aggre) * sum(seg.share * coef_seg[,5] * prob_MB_seg * prob_KR_seg)
cat(sprintf('Cross-price elasticiy of KB and KR under segments is %.2f\nCross-price elasticiy of KB and MB under segments is %.2f\nCross-price elasticiy of KR and KB under segments is %.2f\nCross-price elasticiy of KR and MB under segments is %.2f\nCross-price elasticiy of MB and KB under segments is %.2f\nCross-price elasticiy of MB and KR under segments is %.2f\n', crossElasticity_KBvsKR_seg, crossElasticity_KBvsMB_seg, crossElasticity_KRvsKB_seg, crossElasticity_KRvsMB_seg, crossElasticity_MBvsKB_seg, crossElasticity_MBvsKR_seg))
```
The bigger the cross-price elasticity is, if bigger than zero, the closer the substitutes is. Hence, from the cross-elasticity, MB and KR are the closest substitute while KR and KB are not substitute.

```{r}
# Prob to price plot
# KB
df <- data.frame(pricespace = seq(.01, 3, .01))
df$KB_segment1 <- sapply(df$pricespace, function(x) demand_KB(x, mean(data$price.KR), mean(data$price.MB), coef_seg[1,-1]))
df$KB_segment2 <- sapply(df$pricespace, function(x) demand_KB(x, mean(data$price.KR), mean(data$price.MB), coef_seg[2,-1]))
df$KB_segment3 <- sapply(df$pricespace, function(x) demand_KB(x, mean(data$price.KR), mean(data$price.MB), coef_seg[3,-1]))
df$KB_segment4 <- sapply(df$pricespace, function(x) demand_KB(x, mean(data$price.KR), mean(data$price.MB), coef_seg[4,-1]))
df$KB_segment5 <- sapply(df$pricespace, function(x) demand_KB(x, mean(data$price.KR), mean(data$price.MB), coef_seg[5,-1]))
df$KB_segment6 <- sapply(df$pricespace, function(x) demand_KB(x, mean(data$price.KR), mean(data$price.MB), coef_seg[6,-1]))
df$KB_segment7 <- sapply(df$pricespace, function(x) demand_KB(x, mean(data$price.KR), mean(data$price.MB), coef_seg[7,-1]))
df$KB_segment8 <- sapply(df$pricespace, function(x) demand_KB(x, mean(data$price.KR), mean(data$price.MB), coef_seg[8,-1]))
df$KB_segment9 <- sapply(df$pricespace, function(x) demand_KB(x, mean(data$price.KR), mean(data$price.MB), coef_seg[9,-1]))
df %>%
  e_chart(pricespace) %>%
  e_line(KB_segment1) %>%
  e_line(KB_segment2) %>%
  e_line(KB_segment3) %>%
  e_line(KB_segment4) %>%
  e_line(KB_segment5) %>%
  e_line(KB_segment6) %>%
  e_line(KB_segment7) %>%
  e_line(KB_segment8) %>%
  e_line(KB_segment9) %>%
  e_x_axis(name = 'KB Prices') %>%
  e_y_axis(name = 'Probability of purchase KB')

# KR
df <- data.frame(pricespace = seq(.01, 3, .01))
df$KR_segment1 <- sapply(df$pricespace, function(x) demand_KR(mean(data$price.KB), x, mean(data$price.MB), coef_seg[1,-1]))
df$KR_segment2 <- sapply(df$pricespace, function(x) demand_KR(mean(data$price.KB), x, mean(data$price.MB), coef_seg[2,-1]))
df$KR_segment3 <- sapply(df$pricespace, function(x) demand_KR(mean(data$price.KB), x, mean(data$price.MB), coef_seg[3,-1]))
df$KR_segment4 <- sapply(df$pricespace, function(x) demand_KR(mean(data$price.KB), x, mean(data$price.MB), coef_seg[4,-1]))
df$KR_segment5 <- sapply(df$pricespace, function(x) demand_KR(mean(data$price.KB), x, mean(data$price.MB), coef_seg[5,-1]))
df$KR_segment6 <- sapply(df$pricespace, function(x) demand_KR(mean(data$price.KB), x, mean(data$price.MB), coef_seg[6,-1]))
df$KR_segment7 <- sapply(df$pricespace, function(x) demand_KR(mean(data$price.KB), x, mean(data$price.MB), coef_seg[7,-1]))
df$KR_segment8 <- sapply(df$pricespace, function(x) demand_KR(mean(data$price.KB), x, mean(data$price.MB), coef_seg[8,-1]))
df$KR_segment9 <- sapply(df$pricespace, function(x) demand_KR(mean(data$price.KB), x, mean(data$price.MB), coef_seg[9,-1]))
df %>%
  e_chart(pricespace) %>%
  e_line(KR_segment1) %>%
  e_line(KR_segment2) %>%
  e_line(KR_segment3) %>%
  e_line(KR_segment4) %>%
  e_line(KR_segment5) %>%
  e_line(KR_segment6) %>%
  e_line(KR_segment7) %>%
  e_line(KR_segment8) %>%
  e_line(KR_segment9) %>%
  e_x_axis(name = 'KR Prices') %>%
  e_y_axis(name = 'Probability of purchase KR')

# MB
df <- data.frame(pricespace = seq(.01, 3, .01))
df$MB_segment1 <- sapply(df$pricespace, function(x) demand_MB(mean(data$price.KB), mean(data$price.KR), x, coef_seg[1,-1]))
df$MB_segment2 <- sapply(df$pricespace, function(x) demand_MB(mean(data$price.KB), mean(data$price.KR), x, coef_seg[2,-1]))
df$MB_segment3 <- sapply(df$pricespace, function(x) demand_MB(mean(data$price.KB), mean(data$price.KR), x, coef_seg[3,-1]))
df$MB_segment4 <- sapply(df$pricespace, function(x) demand_MB(mean(data$price.KB), mean(data$price.KR), x, coef_seg[4,-1]))
df$MB_segment5 <- sapply(df$pricespace, function(x) demand_MB(mean(data$price.KB), mean(data$price.KR), x, coef_seg[5,-1]))
df$MB_segment6 <- sapply(df$pricespace, function(x) demand_MB(mean(data$price.KB), mean(data$price.KR), x, coef_seg[6,-1]))
df$MB_segment7 <- sapply(df$pricespace, function(x) demand_MB(mean(data$price.KB), mean(data$price.KR), x, coef_seg[7,-1]))
df$MB_segment8 <- sapply(df$pricespace, function(x) demand_MB(mean(data$price.KB), mean(data$price.KR), x, coef_seg[8,-1]))
df$MB_segment9 <- sapply(df$pricespace, function(x) demand_MB(mean(data$price.KB), mean(data$price.KR), x, coef_seg[9,-1]))
df %>%
  e_chart(pricespace) %>%
  e_line(MB_segment1) %>%
  e_line(MB_segment2) %>%
  e_line(MB_segment3) %>%
  e_line(MB_segment4) %>%
  e_line(MB_segment5) %>%
  e_line(MB_segment6) %>%
  e_line(MB_segment7) %>%
  e_line(MB_segment8) %>%
  e_line(MB_segment9) %>%
  e_x_axis(name = 'MB Prices') %>%
  e_y_axis(name = 'Probability of purchase MB')


#Scatterplot of parameters - beta_0^{KB}-beta_0^{KR} against beta_1.
plot(coef_seg[1,2] - coef_seg[1,3], coef_seg[1,5], cex = 20 * seg.share[1], xlim = c(-3,3), ylim = c(-9,-1.5),
     col = "red", pch = 16, cex.lab = 1.5, cex.axis = 1.5, cex.main = 1.5, cex.sub = 1.5,
     xlab = "beta_0^KB-beta_0^KR", ylab = "beta_1")
points(coef_seg[2,2] - coef_seg[2,3], coef_seg[2,5], cex = 20 * seg.share[2], col = "green",pch = 16)
points(coef_seg[3,2] - coef_seg[3,3], coef_seg[3,5], cex = 20 * seg.share[3], col = "yellow",pch = 16)
points(coef_seg[4,2] - coef_seg[4,3], coef_seg[4,5], cex = 20 * seg.share[4], col = "green",pch = 16)
points(coef_seg[5,2] - coef_seg[5,3], coef_seg[5,5], cex = 20 * seg.share[5], col = "blue",pch = 16)
points(coef_seg[6,2] - coef_seg[6,3], coef_seg[6,5], cex = 20 * seg.share[6], col = "black",pch = 16)
points(coef_seg[7,2] - coef_seg[7,3], coef_seg[7,5], cex = 20 * seg.share[7], col = "purple",pch = 16)
points(coef_seg[8,2] - coef_seg[8,3], coef_seg[8,5], cex = 20 * seg.share[8], col = "pink",pch = 16)
points(coef_seg[9,2] - coef_seg[9,3], coef_seg[9,5], cex = 20 * seg.share[9], col = "orange",pch = 16)


plot(coef_seg[1,2] - coef_seg[1,3], coef_seg[1,2] - coef_seg[1,4], cex = 20 * seg.share[1], xlim = c(-1,1), ylim = c(-1,1),
     col = "red", pch = 16, cex.lab = 1.5, cex.axis = 1.5, cex.main = 1.5, cex.sub = 1.5,
     xlab = "beta_0^KB-beta_0^KR", ylab = "beta_0^KB-beta0^MB")
points(coef_seg[2,2] - coef_seg[2,3], coef_seg[2,2] - coef_seg[2,4], cex = 20 * seg.share[2], col = "green",pch = 16)
points(coef_seg[3,2] - coef_seg[3,3], coef_seg[3,2] - coef_seg[3,4], cex = 20 * seg.share[3], col = "yellow",pch = 16)
points(coef_seg[4,2] - coef_seg[4,3], coef_seg[4,2] - coef_seg[4,4], cex = 20 * seg.share[4], col = "green",pch = 16)
points(coef_seg[5,2] - coef_seg[5,3], coef_seg[5,2] - coef_seg[5,4], cex = 20 * seg.share[5], col = "blue",pch = 16)
points(coef_seg[6,2] - coef_seg[6,3], coef_seg[6,2] - coef_seg[6,4], cex = 20 * seg.share[6], col = "black",pch = 16)
points(coef_seg[7,2] - coef_seg[7,3], coef_seg[7,2] - coef_seg[7,4], cex = 20 * seg.share[7], col = "purple",pch = 16)
points(coef_seg[8,2] - coef_seg[8,3], coef_seg[8,2] - coef_seg[8,4], cex = 20 * seg.share[8], col = "pink",pch = 16)
points(coef_seg[9,2] - coef_seg[9,3], coef_seg[9,2] - coef_seg[9,4], cex = 20 * seg.share[9], col = "orange",pch = 16)
```


```{r}
# Profit in each segment
#KB
profit_KB_seg <- 1000 * demand_KB(mean(data$price.KB), mean(data$price.KR), mean(data$price.MB), coef_seg[,-1]) * (mean(data$price.KB) - .5)
profit_KB_seg
```
According to the scatterplot and profit we calculatein each segment, the optimal segment to launch KB is segment 5 and 9.


When decided not to launch Kiwi Bubbles:
```{r}
df <- data[,-5]
coef_seg_noKB <- data.frame(segment = 1:9, intercept.KR = NA, intercept.MB = NA, price.coef = NA)
for (i in 1:9) {
  data_sub <- subset(df, cluster == i)
  mlogitdata <- mlogit.data(data_sub, id.var = 'id', varying = 4:6, choice = 'choice', shape = 'wide')
  mle <- gmnl(choice ~ price, data = mlogitdata)
  coef_seg_noKB[i, -1] <- mle$coefficients
}
demand_KR_noKB <- function(price_KR, price_MB, param) {
  return(
    exp(param[1] + param[3] * price_KR) / (1 + exp(param[1] + param[3] * price_KR) + exp(param[2] + param[3] * price_MB))
  )
}

pricespace <- seq(.01, 3, .01)
profit_KR_seg_noKB <- 1000 * (seg.share[1] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, 1.43, coef_seg_noKB[1,-1]) * (x - .5))) +
  seg.share[2] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, 1.43, coef_seg_noKB[2,-1]) * (x - .5))) +
  seg.share[3] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, 1.43, coef_seg_noKB[3,-1]) * (x - .5))) +
  seg.share[4] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, 1.43, coef_seg_noKB[4,-1]) * (x - .5))) +
  seg.share[5] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, 1.43, coef_seg_noKB[5,-1]) * (x - .5))) +
  seg.share[6] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, 1.43, coef_seg_noKB[6,-1]) * (x - .5))) +
  seg.share[7] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, 1.43, coef_seg_noKB[7,-1]) * (x - .5))) +
  seg.share[8] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, 1.43, coef_seg_noKB[8,-1]) * (x - .5))) +
  seg.share[9] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, 1.43, coef_seg_noKB[9,-1]) * (x - .5))))

cat(sprintf('The optimal price of KR is %.2f', pricespace[which.max(profit_KR_seg_noKB)]))
```

When do launch Kiwi Bubbles:
```{r}
pricespace_KB <- seq(.01, 3, .01)
pricespace_KR <- seq(.01, 3, .01)


aggre_KB_seg <- function(pricespace_KB, pricespace_KR) {
  1000 * (seg.share[1] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, 1.43, as.numeric(coef_seg[1,-1])) * (x - .5)) +
  seg.share[2] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, 1.43, as.numeric(coef_seg[2,-1])) * (x - .5)) +
  seg.share[3] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, 1.43, as.numeric(coef_seg[3,-1])) * (x - .5)) +
  seg.share[4] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, 1.43, as.numeric(coef_seg[4,-1])) * (x - .5)) +
  seg.share[5] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, 1.43, as.numeric(coef_seg[5,-1])) * (x - .5)) +
  seg.share[6] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, 1.43, as.numeric(coef_seg[6,-1])) * (x - .5)) +
  seg.share[7] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, 1.43, as.numeric(coef_seg[7,-1])) * (x - .5)) +
  seg.share[8] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, 1.43, as.numeric(coef_seg[8,-1])) * (x - .5)) +
  seg.share[9] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, 1.43, as.numeric(coef_seg[9,-1])) * (x - .5)))
}

aggre_KR_seg <- function(pricespace_KB, pricespace_KR) {
  1000 * (seg.share[1] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, 1.43, as.numeric(coef_seg[1,-1])) * (y - .5)) +
  seg.share[2] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, 1.43, as.numeric(coef_seg[2,-1])) * (y - .5)) +
  seg.share[3] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, 1.43, as.numeric(coef_seg[3,-1])) * (y - .5)) +
  seg.share[4] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, 1.43, as.numeric(coef_seg[4,-1])) * (y - .5)) +
  seg.share[5] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, 1.43, as.numeric(coef_seg[5,-1])) * (y - .5)) +
  seg.share[6] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, 1.43, as.numeric(coef_seg[6,-1])) * (y - .5)) +
  seg.share[7] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, 1.43, as.numeric(coef_seg[7,-1])) * (y - .5)) +
  seg.share[8] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, 1.43, as.numeric(coef_seg[8,-1])) * (y - .5)) +
  seg.share[9] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, 1.43, as.numeric(coef_seg[9,-1])) * (y - .5)))
}

KW_profit_seg <- aggre_KB_seg(pricespace_KB, pricespace_KR) + aggre_KR_seg(pricespace_KB, pricespace_KR)

index <- which(KW_profit_seg == max(KW_profit_seg), arr.ind = TRUE)
optimal_KBprice <- pricespace_KB[index[1]]
optimal_KRprice <- pricespace_KR[index[2]]
cat(sprintf('The optimal prices to achieve maximum profit for Kiwi company is to set the price of KB to %.2f and the price of KR to %.2f.', optimal_KBprice, optimal_KRprice))


```

How does the profit of Kiwi and Mango change as Kiwi launches KB?
```{r}
# before
KW_before <- 1000 * sum(apply(coef_seg_noKB[,-1], MARGIN = 1, function(x) demand_KR_noKB(mean(data$price.KR), 1.43, x)) * seg.share) * (mean(data$price.KR - .5))

KW_after <- 1000 * sum(apply(coef_seg[,-1], MARGIN = 1, function(x) demand_KB(mean(data$price.KB), mean(data$price.KR), 1.43, x)) * seg.share) * (mean(data$price.KB - .5)) + 1000 * sum(apply(coef_seg[,-1], MARGIN = 1, function(x) demand_KR(mean(data$price.KB), mean(data$price.KR), 1.43, x)) * seg.share) * (mean(data$price.KR - .5))

demand_MB_noKB <- function(price_KR, price_MB, param) {
  return(
    exp(param[2] + param[3] * price_MB) / (1 + exp(param[1] + param[3] * price_KR) + exp(param[2] + param[3] * price_MB))
  )
}
MB_before <- 1000 * sum(apply(coef_seg_noKB[,-1], MARGIN = 1, function(x) demand_MB_noKB(mean(data$price.KR), 1.43, x)) * seg.share) * (mean(data$price.KR - .5))

MB_after <- 1000 * sum(apply(coef_seg[,-1], MARGIN = 1, function(x) demand_MB(mean(data$price.KB), mean(data$price.KR), 1.43, x)) * seg.share) * (mean(data$price.MB - .5))

df <- data.frame(time = c('before', 'after'))
df$KW[df$time == 'before'] <- KW_before
df$KW[df$time == 'after'] <- KW_after
df$MB[df$time == 'before'] <- MB_before
df$MB[df$time == 'after'] <- MB_after
df %>%
  e_charts(time) %>%
  e_bar(KW) %>%
  e_bar(MB) %>%
  e_y_axis(name = 'Profit')

```
Yes, we should launch KB. The first reason is KW's profit is higher with KB and the profit of MB is lower with KB. Second, as we know, KR and KB are not close subsitute which means customers have two different options instaed of buying one and dropping the other. Hence, introducing KB to market is the best option.

## Q5: Understanding strategic responses
```{r}
MB_fun <- function(optimal_KBprice, optimal_KRprice) {
  pricespace <- seq(.01, 3, .01)
  profit_MB <- sapply(pricespace, function(x) 1000 * sum(seg.share * apply(coef_seg[,-1], 1, function(y) demand_MB(optimal_KBprice, optimal_KRprice, x, y) * (x - .5))))
  MB_newprice <- pricespace[which.max(profit_MB)]
  return(MB_newprice)
}

KW_fun <- function(z) {
  pricespace_KB <- seq(.01, 3, .01)
  pricespace_KR <- seq(.01, 3, .01)
  aggre_KB_seg <- function(pricespace_KB, pricespace_KR) {
    1000 * (seg.share[1] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, z, as.numeric(coef_seg[1,-1])) * (x - .5)) +
    seg.share[2] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, z, as.numeric(coef_seg[2,-1])) * (x - .5)) +
    seg.share[3] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, z, as.numeric(coef_seg[3,-1])) * (x - .5)) +
    seg.share[4] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, z, as.numeric(coef_seg[4,-1])) * (x - .5)) +
    seg.share[5] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, z, as.numeric(coef_seg[5,-1])) * (x - .5)) +
    seg.share[6] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, z, as.numeric(coef_seg[6,-1])) * (x - .5)) +
    seg.share[7] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, z, as.numeric(coef_seg[7,-1])) * (x - .5)) +
    seg.share[8] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, z, as.numeric(coef_seg[8,-1])) * (x - .5)) +
    seg.share[9] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KB(x, y, z, as.numeric(coef_seg[9,-1])) * (x - .5)))
  }
  aggre_KR_seg <- function(pricespace_KB, pricespace_KR) {
    1000 * (seg.share[1] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, z, as.numeric(coef_seg[1,-1])) * (y - .5)) +
    seg.share[2] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, z, as.numeric(coef_seg[2,-1])) * (y - .5)) +
    seg.share[3] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, z, as.numeric(coef_seg[3,-1])) * (y - .5)) +
    seg.share[4] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, z, as.numeric(coef_seg[4,-1])) * (y - .5)) +
    seg.share[5] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, z, as.numeric(coef_seg[5,-1])) * (y - .5)) +
    seg.share[6] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, z, as.numeric(coef_seg[6,-1])) * (y - .5)) +
    seg.share[7] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, z, as.numeric(coef_seg[7,-1])) * (y - .5)) +
    seg.share[8] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, z, as.numeric(coef_seg[8,-1])) * (y - .5)) +
    seg.share[9] * outer(pricespace_KB, pricespace_KR, function(x, y) demand_KR(x, y, z, as.numeric(coef_seg[9,-1])) * (y - .5)))
  }
  KW_profit_seg <- aggre_KB_seg(pricespace_KB, pricespace_KR) + aggre_KR_seg(pricespace_KB, pricespace_KR)
  index <- which(KW_profit_seg == max(KW_profit_seg), arr.ind = TRUE)
  optimal_KBprice <- pricespace_KB[index[1]]
  optimal_KRprice <- pricespace_KR[index[2]]
  return(c(optimal_KBprice, optimal_KRprice))
}


MB_price <- 1.43
MB <- numeric()
KW <- list()
for (i in 1:20) {
  KW_price <- KW_fun(MB_price)
  KW <- c(KW, list(KW_price))
  MB <- c(MB, MB_price)
  MB_price <- MB_fun(KW_price[1], KW_price[2])
}


df <- data.frame(t = 1:20, MB = MB, KW.KB = sapply(KW, function(x) x[1]), KW.KR = sapply(KW, function(x) x[2]))

df %>% e_charts(t) %>% e_line(MB) %>% e_line(KW.KB) %>% e_line(KW.KR)

MB_price_withKB <- df$MB[length(df$MB)]
KB_price_withKB <- df$KW.KB[length(df$KW.KB)]
KR_price_withKB <- df$KW.KR[length(df$KW.KR)]
MB_price_withKB
KB_price_withKB
KR_price_withKB
```
The final convergence result are the price of MB is 0.91, the price of KB is 1, the price of KR is 1.07.

```{r}
# Calculate KW profit when there is no KB under price war
KW_fun_noKB <- function(z) {
  pricespace <- seq(.01, 3, .01)
  profit_KR_seg_noKB <- 1000 * (seg.share[1] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, z, coef_seg_noKB[1,-1]) * (x - .5))) +
    seg.share[2] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, z, coef_seg_noKB[2,-1]) * (x - .5))) +
    seg.share[3] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, z, coef_seg_noKB[3,-1]) * (x - .5))) +
    seg.share[4] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, z, coef_seg_noKB[4,-1]) * (x - .5))) +
    seg.share[5] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, z, coef_seg_noKB[5,-1]) * (x - .5))) +
    seg.share[6] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, z, coef_seg_noKB[6,-1]) * (x - .5))) +
    seg.share[7] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, z, coef_seg_noKB[7,-1]) * (x - .5))) +
    seg.share[8] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, z, coef_seg_noKB[8,-1]) * (x - .5))) +
    seg.share[9] * unlist(sapply(pricespace, function(x) demand_KR_noKB(x, z, coef_seg_noKB[9,-1]) * (x - .5))))
  index <- which(profit_KR_seg_noKB == max(profit_KR_seg_noKB))
  optimal_KRprice <- pricespace[index]
  return(optimal_KRprice)
}

MB_fun_noKB <- function(optimal_KRprice) {
  pricespace <- seq(.01, 3, .01)
  profit_MB <- sapply(pricespace, function(x) 1000 * sum(seg.share * apply(coef_seg_noKB[,-1], 1, function(y) demand_MB_noKB(optimal_KRprice, x, y) * (x - .5))))
  MB_newprice <- pricespace[which.max(profit_MB)]
  return(MB_newprice)
}

MB_price <- 1.43
MB <- numeric()
KW <- numeric()
for (i in 1:20) {
  KW_price <- KW_fun_noKB(MB_price)
  KW <- c(KW, KW_price)
  MB <- c(MB, MB_price)
  MB_price <- MB_fun_noKB(KW_price)
}

df <- data.frame(t = 1:20, MB = MB, KW.KR = KW)

#df %>% e_charts(t) %>% e_line(MB) %>% e_line(KW)

cat(sprintf('The final convergence result are the price of MB is %.2f, the price of KR is %.2f.', df$MB[length(df$MB)], df$KW[length(df$KW)]))

MB_price_noKB <- df$MB[length(df$MB)]
KR_price_noKB <- df$KW[length(df$KW)]

```

```{r}
# Profit under price war

# before
KW_before <- 1000 * sum(apply(coef_seg_noKB[,-1], MARGIN = 1, function(x) demand_KR_noKB(KR_price_noKB, MB_price_noKB, x)) * seg.share) * (KR_price_noKB - .5)

KW_after <- 1000 * sum(apply(coef_seg[,-1], MARGIN = 1, function(x) demand_KB(KB_price_withKB, KR_price_withKB, MB_price_withKB, x)) * seg.share) * (KB_price_withKB - .5) + 1000 * sum(apply(coef_seg[,-1], MARGIN = 1, function(x) demand_KR(KB_price_withKB, KR_price_withKB, MB_price_withKB, x)) * seg.share) * (KR_price_withKB - .5)

MB_before <- 1000 * sum(apply(coef_seg_noKB[,-1], MARGIN = 1, function(x) demand_MB_noKB(KR_price_noKB, MB_price_noKB, x)) * seg.share) * (KR_price_noKB - .5)

MB_after <- 1000 * sum(apply(coef_seg[,-1], MARGIN = 1, function(x) demand_MB(KB_price_withKB, KR_price_withKB, MB_price_withKB, x)) * seg.share) * (MB_price_withKB - .5)

df <- data.frame(time = c('before', 'after'))
df$KW[df$time == 'before'] <- KW_before
df$KW[df$time == 'after'] <- KW_after
df$MB[df$time == 'before'] <- MB_before
df$MB[df$time == 'after'] <- MB_after
df %>%
  e_charts(time) %>%
  e_bar(KW) %>%
  e_bar(MB) %>%
  e_y_axis(name = 'Profit')

```
Under the "pricing war" scenario, KW only has a small advatantages in profit compared to MB's profit which is 189 vs 179. However, after lauching the Kiw Bubbles, our profit advantages become much higher which is 260 vs 143. So we definetely get more market shares and target for more customers, I think it's a good stratetic to lauch Kiwi Bubbles.